\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\label{acknowledgements}
\setheader{Acknowledgements}

These last 4-5 years have been truly transformative and I feel extremely grateful for how much I could learn, grow, and have real fun. For this, I would like to thank a number of people who I was lucky to meet along the way. \\[0.5pt]

\noindent First of all I would like to thank my promotor, \textbf{Cees}. Thank you for giving me the opportunity to join the cool CD lab. I feel extremely lucky I could learn from you the way to \emph{do science}. %I can now say that I am not surprised for your achievements and academic success, as I had the chance to see with my eyes what it takes to be at your level. 
You tremendously shaped the way I do research: from conceiving a project, to carry out experiments and write a story about it (including making nice figures). I learned that to do meaningful science, technique(s) should serve the scientific question, and not the other way around. In fact, to find answers to my questions I was able to explore freely and master a wide array of techniques, from making electrical measurements on biomimetic nanopores, up to looking at giant liposomes through a confocal microscope. Conceiving original ideas is key to any great innovation and discovery, and you showed me that boldness and a pinch of naivety are very important in such process, as we would have never made our beloved `designer FG-Nups' otherwise. I am grateful for the numerous supportive, exciting, and confidence boosting meetings, which made me even more motivated and ambitious to achieve always higher goals. Finally, I really enjoyed our casual, fun chats, competing against each other on the football court, as well as jamming together on multiple occasions – still impressed, and a bit jealous, of how many different instruments you can play.\\[0.5pt]

\noindent I would like to thank the committee members for taking the time to read and assess my thesis: \textbf{Prof. Anton Zilman}, \textbf{Prof. Roderick Lim}, \textbf{Prof. Marileen Dogterom}, \textbf{Prof. Patrick Onck}, \textbf{Prof. Liesbeth Veenhoff}, \textbf{Dr. Sabina Caneva}. I hope you found it interesting and I look forward to the discussion.\\[0.5pt]

\noindent One of the best aspects of academia is discussing your research with peers who share the same curiosity and enthusiasm. Throughout the years, I had the fortune to engage in a number of successful collaborations and team efforts. \noindent \textbf{Henry}, I still remember our first virtual meetings when we were both starting our PhD. Conceiving the idea of designing new FG-Nups from scratch with you has been really exciting. It was the first time in my PhD where I felt like `we had it', a true \emph{eureka} moment, while dreaming about all possible applications and future impact. I learned a lot from you. You are accurate, calm, and reflective, which by the way helped a lot while preparing the rebuttals for Rev.\#4. I'm so happy that, in the end, we made it! \textbf{John} and \textbf{Andreas}, I really enjoyed collaborating with you and I really appreciated your positive energy and swift reaction to our proposal of collaboration. Your contribution has been (and still is) extremely valuable. \textbf{Pierre} and \textbf{Hendrik}, the best DNA-origami architects I know. I had so much fun working with your nanostructures and I am very proud of our shared work.\\[0.5pt]

\noindent In the CD lab I found many people who inspired me on a both scientific and personal level. Notable mentions go to the nanopore/NPC team.
\textbf{Sergii}, thank you for all the noisy discussions, it has been so much fun. You have been truly inspirational and I always admired your sharpness and creativity. \textbf{Sonja}, I still remember the myriads of nanopore sketches I drew on the wall in your office. Many great discussions, sometimes extremely long and tiring, but thanks to that nanopores have now much less secrets. I was always impressed by the quality of your work (and your slides!), your innate stubbornness and genuine curiosity, as well as your ultrabroad skillset. \textbf{Adi}, thanks for handing me the legacy of biomimetic NPCs, your lessons and ground work helped me a lot in getting through the rough world of nanopores. \textbf{Wayne}, thanks for being such a cool nanopore buddy. Your jokes and dark humour made my life in the lab much more enjoyable. Also, thanks for your precious help in making this thesis! \textbf{Daniel V}, it was really fun to have you around, I still wonder where you get all that energy. I was always struck by your natural charisma, and I was a big fan of your Christmas presentations, simply brilliant. \textbf{Daniel Shi}, I admire how you get so much work done all by yourself. I really enjoyed our beer drinking sessions and fun conversations. \textbf{Laura}, I will only say one number: 549! I know you will understand. \textbf{Stephanie}, thanks for the nice chats in the office and for sharing your noisy data. Your graphene pores definitely won the battle for the highest 1/f noise. \textbf{Paola}, it was great to have a NPC biologist in the team who is aware of how good food should taste like. \textbf{Nils}, you are unique in so many aspects and I truly admire how you pursue your ideals regardless of what all the others think or do. Social pressure clearly has no effect on your decisions. \textbf{Anders}, I only wish you had joined the lab much earlier on, I really love working as well as rocking together.\\[0.5pt]

\noindent The work presented in this thesis would have not been nearly possible without the help of some really skilled people. \textbf{Eli}, your contribution to this thesis is just enormous. Thank you for all the proteins you made and purified (the list is very long) and for helping me in the design and making of our designer Nups. I am sorry that those were such a pain to express, but your stubbornness won eventually! I am grateful for all the lab skills and tricks I could learn from you, and thanks a lot for translating my summary. \textbf{Ash}, thank you so much for all the proteins (sorry for the NupYs!), still impressed how organized and efficient you are at doing what you are doing. Most importantly, I love your voice, our crazy singing sessions, and our duets, such emotional moments! \textbf{Jaco}, you helped me out and gave really useful advice in so many circumstances. It was always fun to chat in the lab and discuss my latest data with you. \textbf{Meng-Yue}, thank you for supplying top quality nanopores to all of us and for accommodating our demands on many occasions. \textbf{Wiel}, thanks for assisting me in operating the TEM and for all the sarcastic jokes. \textbf{Allard}, thank you for taking the coolest images ever of our Nup-coated DNA-origami pores, your AFM skills are just superior. I still keep that dataset for when I need to show off. \textbf{Jacob}, we managed to finally collaborate on a shared project during my last year and I can't thank you enough for the coding tricks and ideas you taught me, as well as all the laughs and jokes we had while debugging. \textbf{Jeremie}, thank you for assisting me in operating the confocal microscope.  \textbf{Dimitri} and \textbf{Jelle}, the best craftsmen at TU Delft, thank you for realizing many awesome flow cells and chip holders, your work made my life in the lab so much easier. \textbf{Amanda} and \textbf{Jan}, thank you so much for helping me out with all the paperwork. \textbf{ICT people}, thank you for keeping my Mac alive throughout all these years. \\[0.5pt]

\noindent Optimizing protocols can be very challenging and time consuming. Luckily for me, I had the opportunity to guide and mentor many talented bachelor and master students who contributed greatly to the making of this thesis. \textbf{Allison}, you were my first student who courageously embarked in one of my projects. I am so happy of how it went, your QCM-D ground work was essential to many of our follow up projects, including the NupX paper. Most importantly, we had such a great time! I think I never laughed so hard in the lab, I still feel a bit sorry for Andrea's TEM grids. \textbf{Andrea}, wei Bomber! I was (and still am) so proud of my italian student prodigy. I admired your exceptional creativity, instinct, motivation, and independence. You literally nailed every single project I gave you, hats off to you. \textbf{Madusha}, working with you has been a privilege and I feel extremely lucky I had you as one of my students. You are incredibly fast learning, skillful, and diligent, and you managed to explore so many uncharted territories with our DNA-origami pores in such a short period of time.  \textbf{Tong}, I won't deny you had one of the most challenging projects for a student, but you managed to produce cool results nonetheless. I really appreciated our discussions, I could see how you really enjoyed contemplating about the physics underlying our nanopore experiments. \textbf{Bloem}, I am still dazzled by your impeccable work and total independence. You learned the technique in one go, almost effortlessly, and you never screwed up an experiment. Thank you for all the great work. Last but not least, \textbf{Johanna}! I am really fond of your enthusiasm for science and contagious smile. I value greatly your sharp, inquisitive, and critical mind, and thanks for reporting the mistakes in our paper, which none of the reviewers could find instead.\\[0.5pt]

\noindent Aside for the great science, I had the pleasure to share numerous nice moments with many people around the lab. \textbf{Sandro}, you have been great colleague, an incredibly chilled though prolific scientist, and a great friend (don't get too emotional now). I have fond memories of the several band practices, BN concerts, fussball games, and some crazy nights. \textbf{Albertone}, the sexiest (e)spanish I know. You have been the best buddy I could wish for, and we shared such beautiful moments together. Besides preparing all those litres of sangria in portugal, I loved to engage in philosophical discussions with you. Grande \textbf{Fede} \#1! I have many fond memories of our numerous concerts and fun moments in the office. You were hands down the toughest competitor at fussball. \textbf{JK}, a.k.a. \emph{Dr. Love}, you are so cool. I loved playing with you and thank you for being so supportive and enthusiastic about my research and ideas. \textbf{Eugene}, I really enjoyed sharing so many beers together (you are a tough competitor (also) in that area!) and some really fun moments in San Diego. \textbf{Bis}, I admire your calm, always positive, relaxed temper. \textbf{Oskar}, your viking, ferocious spirit managed to take me down once, but one day I will get my revenge! \textbf{Kuba}, you are so Ridiculo! I loved your fine sense of humour and thanks for being my fussball mentor. \textbf{Nicola}, it was great to discuss DNA origami in \emph{dialetto veneto} and I'm proud of the awesome paper we had together. \textbf{Ganji}, you will be remembered as the first nano-looper, I enjoyed many fun conversations and extremely brutal fussball games. \textbf{Anthony}, thank you for the after work whiskey. \textbf{Richard}, I really enjoyed our chats and complaining about academia. \textbf{Pinyao}, \textbf{Alejandro}, \textbf{Greg}, \textbf{Jorine}, \textbf{Michel}, \textbf{Mitasha}, thanks for the nice moments and fun chats. The next generation: \textbf{Martin}, \textbf{Milos}, \textbf{Roman}, \textbf{Sabrina}, despite the start of your PhD coincided with the start of a global pandemic your motivation and drive has not been nearly affected – I'm confident that the future of the CD lab is in good hands!\\[0.5pt]

\noindent Moments of frustration and stress were relieved at the fussball table, where many fierce games took place. There, I had the pleasure to fight against some really good players from BN: \textbf{Luuk}, \textbf{Tijs}, \textbf{David}, \textbf{Elisa}, \textbf{Duko}, \textbf{Benjamin}, thank you for sharing the field with me. From the rest of BN, I would like to thank \textbf{Mike} for the nice chats in the lab corridors about science and Netflix gangster series, \textbf{Helena}, \textbf{Becca}, and \textbf{Viktorija} for the great parties and dancing, \textbf{Jochem}, for sharing the passion for SRV, \textbf{Tanja} for the fun conversations and imaging our grids, \textbf{Sam} and \textbf{Misha} for the great times playing together. I thank professors \textbf{Marie-Eve} for being extremely supportive and \textbf{Arjen} for the scientific discussions. I would also like to thank \textbf{Erik} for making such a cool cover for my thesis!\\[0.5pt]

\noindent Despite living abroad for so many years, where the sunlight is as scarce as the taste of a raw zucchini,  I managed to feel less nostalgic thanks to some good Southern European friends: \textbf{Luca}, thanks preparing Carbonara with \emph{real} Guanciale. \textbf{Omar}, \textbf{Sasi}, \textbf{Beppe}, thank you for the parties \emph{all'italiana} and off-beat jam sessions. \textbf{Fede} and \textbf{Giulia}, thanks for inviting me to your place for dinner and play gypsy jazz. \textbf{Giulio}, the best barber I know, I'm so honoured I could contribute to the creation of the Schiedam crop. \textbf{Filipe}, my awesome vocal coach, thank you for bringing so much passion into every class. \textbf{Maria} and \textbf{Dimitri}, thank you for providing the best homemade, heartwarming food one can find on campus. \\[0.5pt]

\noindent Voglio ringraziare la mia famiglia. \textbf{Mamma} e \textbf{Pap\`a}, grazie per avermi supportato durante i miei lunghi anni di studi, sia economicamente (ricorder\`o per sempre i sacrifici per mandarmi a Boston!), ma sopratutto spiritualmente. La mia motivazione, determinazione e ambizione la devo a voi e ai vostri stimoli. Ma soprattutto vi ringrazio per avermi sempre amato, donandomi un'infanzia e adolescenza felici, senza traumi, non avrei potuto chiedere di meglio! Inoltre, sono grato di avere dei genitori cos\`i fighi e \emph{vivi}, mi avete fatto scoprire e apprezzare tante gioie della vita. \textbf{Alby}, ciao fra! Sappiamo tutti che il tuo contributo \`e stato fondamentale per farmi studiare all'estero, quindi questa tesi la dedico anche a te. In pi\`u occasioni mi hai dimostrato che ho un fratello che mi copre le spalle quando ne ho bisogno, grazie per esserci stato. \\
Infine, \textbf{Gaia}, il mio cucciolone preferito. Scrivo mentre stai per prendere l'ennesimo volo Copenhagen-Amsterdam, che mostra quanto nonostante il mondo cerchi di separarci in mille modi, l'amore che ci tiene uniti vince su tutto. Grazie per avermi supportato, sopportato, spronato, consolato, e incoraggiato costantemente durante questo lungo PhD, sei stata il sostegno che mi ha fatto rialzare nei momenti pi\`u difficili, e il premio pi\`u grande quando c'era da festeggiare per le nostre (tante) vittorie. Insieme siamo invincibili, un team perfetto, affiatati e affamati di conquista. Sono fortunato di avere una persona cos\`i speciale al mio fianco e, come dico sempre, sei la cosa pi\`u bella che esista!\\

\hfill \emph{Alessio Fragasso}

