\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\setheader{List of Publications}
\label{publications}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\begin{etaremune}{\small
\item \underline{\smash{A. Fragasso}}, C. Dekker. \textit{Studying Karyopherins occupancy in the nuclear pore complex using biomimetic nanopores}, {manuscript in preparation}.	
\item Y. Ying*, Z. Hu*, S. Zhang*, Y. Qing*, \underline{\smash{A. Fragasso*}}, X. Zhang*, G. Maglia, A. Meller, H. Bayley, C. Dekker, L. Jiang, Y. Long. \textit{Nanopores: Beyond DNA Sequencing}, manuscript in preparation for \textbf{Nature Nanotechnology}, (commissioned).		
\item \underline{\smash{A. Fragasso*}}, N. De Franceschi*, P. Stoemmer*, E. O. Van der Sluis, H. Dietz, C. Dekker. \textit{Reconstitution of ultrawide DNA origami pores in liposomes for transmembrane transport of macromolecules}, \textbf{ACS Nano}, 15(8), 12768-12779 (2021).
\item \underline{\smash{A. Fragasso*}}, H. W. De Vries*, J. Andersson, E. O. Van Der Sluis, E. Van Der Giessen, A. Dahlin, P. R. Onck, C. Dekker. \textit{A designer FG-Nup that reconstitutes the selective transport barrier of the nuclear pore complex}, \textbf{Nature Communications}, 12(1), 1–15 (2021).
\item \underline{\smash{A. Fragasso}}, S. Schmid, C. Dekker. \textit{Comparing current noise in biological and solid-state nanopores}, \textbf{ACS nano}, 14(2), 1338-1349 (2020).
\item \underline{\smash{A. Fragasso}}, S. Pud, C. Dekker. \textit{1/f noise in solid-state nanopores is governed by access and surface regions}, \textbf{Nanotechnology}  30(39), 395202 (2019).
\item M. Rocca*, \underline{\smash{A.Fragasso*}}, W. Liu, M. A Heinrich, Y. S. Zhang. \textit{Embedded multimaterial extrusion bioprinting}, \textbf{SLAS Technology}, 23(2), 154-163 (2018).
\item W. Liu, Z. Zhong, N. Hu, Y. Zhou, L. Maggio, A. K. Miri, \underline{\smash{A. Fragasso}}, X. Jin, A.Khademhosseini, and Y. S. Zhang. \textit{Coaxial extrusion bioprinting of 3D microfibrous constructs with cell-favorable gelatin methacryloyl microenvironments}, \textbf{Biofabrication}, 10, 024102 (2018).
}\end{etaremune}

\blfootnote{* denotes equal contribution}
